Models of lens candidates from Space Warps CFHTLS

### 2016-12-12 parts/intro.tex
edits

\begin{itemize}
\item Morphology from Figure~\ref{fig:markedup}.
\begin{itemize}
\item The image morphology concisely described: D for double, and
  quads in sub-categorised in four ways
  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
  SW28), SQ for short-axis quads (as in Figure~SW02,
  SW09, SW29, SW42), IQ for inclined quads
  (as in Figure~SW05) and CQ for very symmetric core quads.
\item Whether the images are unblended.  Distinct unblended images (as
  in Figures~SW05 and SW42) are an advantage in
  modelling, but not essential.
\item Whether all images are discernable.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible.  For example, in Figure~SW58,
  the modeller has put in a conjectural saddle point near the lensing
  galaxy.
\item Whether the lens is fairly isolated.
\end{itemize}
\item Mass model
\begin{itemize}
\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
\item Whether the arrival-time surface and synthetic image are
  plausible.  For SW36 the model implies extra images or a long arc,
  which are not seen.  Figures~\ref{fig:arriv} and \ref{fig:synth}.
\end{itemize}
\item Stellar mass. Figure~\ref{fig:stelmass}.
\end{itemize}

Section~\ref{sec:spl} summarises the SpaghettiLens system and
discusses its ongoing development. A SpaghettiLens model consists of a
statistical ensemble of free-form maps of the sky-projected mass
distribution responsible for lensing.  Each lens candidates in
practice gets modelled several times in a collaborative refinement
process\footnote{See ``Collaborative gravitational lens
  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
  the model tree.}  In this paper we report the most recent model for
each lens, as representing a consensus among modellers, as to the best
that could be achieved with the available data and software.
Photometric lens redshifts are used; source redshifts are set to
$z=2$ unless an unambiguous photometric redshift is available.
The models can, however, be trivially rescaled to use better
redshift values, as and when they become available.
\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
identified some areas for improvement.  The first two of those are
taken up in Section~\ref{sec:spl}, along with a further idea. In
\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
profiles of the source.  This feature has not yet been included in
SpaghettiLens, but has been carried out in post-processing for a few
especially interesting candidates.  In \S~\ref{subsec:hires} we show
that making mass maps fine-grained in the central region relieves a
tendency in the earlier work for mass to be too shallow. Then in
\S~\ref{subsec:parameter} we consider the possibility of fitting a
parametric lens model to the model ensemble; so far we have only been
successful at extracting an Einstein radius.

Section~\ref{sec:stellar-mass} explains how we compare the lensing
mass with the mass in stars in the lensing galaxy.  We estimate the
stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
with the well-known stellar-population models of
\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
a halo mass using the abundance-matching prescription of
\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
than the stellar mass but no more than the total halo mass.  We then
introduce what we call a halo index $\haloindex$ which gives an idea
of how the lensing mass compares with these two bounds.

Section~\ref{sec:examples} discusses ten of the systems, including six
systems we found to be particularly interesting.  The online
supplement gives results for all the modelled systems.

>>>>

Purpose is twofold.  First, see if plausible mass models can produce
the overall configuration.  Second, interpretation as lensing
galaxies.  Introduce some diagnostics.

Each lens candidates in practice gets modelled several times in a
collaborative refinement process.\footnote{See ``Collaborative
  gravitational lens modelling\dots'' in {\tt
    http://letters.zooniverse.org} especially the model tree.}  This
representing a consensus among modellers, as to the best that could be
achieved with the available data and software.\footnote{This is in
  contrast to the main Space~Warps project for discovering lenses, in
  which volunteers in a crowd of $\gtrsim10^4$ make independent
  contributions.  Each person is presented with a random selection of
  survey-patches and invited to (in effect) vote on each.  The system
  estimates each volunteer's skill level according to test-patches
  interspersed with the real data, and weights their votes accordingly
  \citep{2016MNRAS.455.1171M}.  There is an active forum for
  volunteers, but since everyone is seeing different data samples with
  minimal overlap, the forum has little if any influence on votes.}

\begin{itemize}
\item Section~\ref{sec:morph} discusses nine of the systems, including
  six systems we found to be particularly interesting.  Morphology
  from Figure~\ref{fig:markedup}.
\begin{itemize}
\item The image morphology concisely described: D for double, and
  quads in sub-categorised in four ways
  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
  SW28), SQ for short-axis quads (as in Figure~SW02,
  SW09, SW29, SW42), IQ for inclined quads
  (as in Figure~SW05) and CQ for very symmetric core quads.
\item Whether the images are unblended.  Distinct unblended images (as
  in Figures~SW05 and SW42) are an advantage in
  modelling, but not essential.
\item Whether all images are discernable.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible.  For example, in Figure~SW58,
  the modeller has put in a conjectural saddle point near the lensing
  galaxy.
\item Whether the lens is fairly isolated.
\end{itemize}
\item Section~\ref{sec:massmodels}
\begin{itemize}
\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
\item Whether the arrival-time surface and synthetic image are
  plausible.  For SW36 the model implies extra images or a long arc,
  which are not seen.  Figures~\ref{fig:arriv} and \ref{fig:synth}.
\end{itemize}
\item Section~\ref{sec:stellar-mass} explains how we compare the lensing
mass with the mass in stars in the lensing galaxy.  We estimate the
stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
with the well-known stellar-population models of
\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
a halo mass using the abundance-matching prescription of
\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
than the stellar mass but no more than the total halo mass.  We then
introduce what we call a halo index $\haloindex$ which gives an idea
of how the lensing mass compares with these two bounds.
Figure~\ref{fig:stelmass}.
\end{itemize}

In this paper we report the most recent model for each lens, as

Section~\ref{sec:summary} builds Table~\ref{tab:models}.
The online supplement gives results for all the modelled systems.

Appendices devoted to various technical issues relating to modelling.
\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
identified some areas for improvement.
In \S~\ref{subsec:sourcefit} we introduce fitting of the brightness
profiles of the source.  This feature has not yet been included in
SpaghettiLens, but has been carried out in post-processing for a few
especially interesting candidates.  In \S~\ref{subsec:hires} we show
that making mass maps fine-grained in the central region relieves a
tendency in the earlier work for mass to be too shallow. Then in
\S~\ref{subsec:parameter} we consider the possibility of fitting a
parametric lens model to the model ensemble; so far we have only been
successful at extracting an Einstein radius.

### 2016-12-12 parts/spl.tex
edits

\section{SpaghettiLens}\label{sec:spl}

SpaghettiLens is an example of a medium-sized collaboration spawned by
a large citizen-science project (in this case Space~Warps).  While
collaboration with volunteers is essential to both, the form of
collaboration is very different.  In Space~Warps, volunteers in a
crowd of $\gtrsim10^4$ make independent contributions.  Each person is
presented with a random selection of survey-patches and invited to (in
effect) vote on each.  The system estimates each volunteer's skill
level according to test-patches interspersed with the real data, and
weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There is
an active forum for volunteers, but since everyone is seeing different
data samples with minimal overlap, the forum has little if any
influence on votes.  With SpaghettiLens, on the other hand, there is a
small group of volunteers and their contributions are interdependent.

A modeller's main input to SpaghettiLens is a sketch of arrival-time
contours on a lensed system.  It gives the locations (or best-guess
locations) of images of point-like sources, along with their ordering
in arrival time, and their parities (minumum, saddle-point or
maximum).  Such a sketch, which we call a spaghetti diagram, tends to
resemble the form of lensed arcs, but it also in effect 
encodes a proposal for its mass distribution.  A spaghetti diagram is
read by a server-side numerical engine \citep[GLASS, developed
  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
of mass maps.  The mass maps are made up of mass tiles and are
free-form, except that they are required to be concentrated around the
identified lens centre.  They are also required to reproduce the given
image locations, parities and time ordering exactly.  Graphical
representations of the mass map and arrival-time surface are returned
to the user for review.  The user can post these results on a forum,
or discard them and try again.  Volunteers can start the modelling
process afresh, or they can take an existing model from the forum and
modify its input spaghetti diagram or its accompanying options, and
thus obtain a revised model.

>>>>

\section{Characterising the lens models}\label{sec:diag}
